%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {XPERI Corporation (DTS)} % Organization
    {Taipei, Taiwan} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Optimized UI performance by implementing MVVM architecture and RecyclerView caching, eliminating frame drops during data updates.}
        \item {Architected custom Android system services for SoftAP, enhancing Wi-Fi network connection stability on embedded hardware platforms.}
        \item {Engineered RTP/RTCP streaming protocols for DTS Play-Fi, enabling low-latency multi-channel wireless audio synchronization.}
        \item {Implemented a Linux process to process system audio PCM data via Unix Domain Sockets, ensuring low-latency audio on Android TV platforms.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Programmer} % Job title
    {XRSPACE Inc.} % Organization
    {Taipei, Taiwan} % Location
    {Mar. 2019 -- Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Led a team of 4 engineers to deliver core VR features; coordinated cross-functional technical tracks to maximize development efficiency.}
        \item {Reduced VR-to-TV streaming latency by customizing SurfaceFlinger and SurfaceView layers to selectively cast VR content via Miracast.}
        \item {Developed a secure, low-overhead Bluetooth library for HMD-to-mobile connectivity, implementing custom protocols and data encryption.}
        \item {Optimized system stability and eliminated UI thread bottlenecks by pinning critical VR processes using CPU affinity techniques and Systrace analysis.}
        %\item {Lead team members (~4 people) to reach the project tasks.}
        %\item {Coordinated and host task topics for cross-team collaboration to decrease unnecessary effort.}
        %\item {Developed a library that connects between HMD and mobile device using BT module, which customized encryption/cryption and packet.}
        %\item {Customized SurfaceView/SurfaceFlinger to cast specified layers of VR content from a foreground VR applicatoin to TV by Miracast.}
        %\item {Implemented a library dedicating specified CPU to a particular process or function by using the technique of CPU affinity.}
        %\item {Experienced with analyzing the system performance and stability using cmd tools/systrace/Android profiler.}
        %\item {Experienced with fine-tuning an application performance for UI rendering with systrace.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Sep. 2018 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated Qualcomm VR and Android Camera NDK to ingest multi-channel feeds (mono, RGB, depth) for 6-DoF tracking algorithms.}
        \item {Engineered a zero-copy Ring Buffer utilizing ashmem  for high-throughput camera frame transmission to Java/Unity layers.}
        \item {Designed high-performance preview windows via ANativeWindow to render 10-bit Raw RGB and YUV-420 formats at stable frame rates.}
        \item {Architected the core wireless communication architecture between VR headsets and Android smartphones using Bluetooth LE.}
        % \item {Developed camera (mono, RGB, depth) getting from QVR (Qualcomm VR solution) and Android Camera NDK for VR 6-Dof processing.}
        % \item {Implemented a Ring Buffer data structure to store camera frame and transmit it to clients (Java/Unity layers) through ashmem or fd.}
        % \item {Designed a preview window tool by ANativeWindow to display camera frame using YUV-420/10-bit Raw RGB format.}
        % \item {Designed communication architecture between VR headset and Android phone using Bluetooth LE.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {ASUSTeK Computer Inc.} % Organization
    {Taipei, Taiwan} % Location
    {Dec. 2015 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {[Zenbo Junior]Developed the behavior of "Line Following" feature with PID control algorithm.}
        % \item {[Zenbo]Developed RobotAPI and RobotSDK for 3rd Developer based on Android Framework.}
        % \item {[Zenbo]Developed the behavior of moving to Docking charger and integrate MCU command for charger control.}
        % \item {[Zenbo]Integrated Battery/Facial/Motion features of main functions using Android Service to RobotFramework.}
        % \item {[Zenbo]Android BSP development - integrate motion sensors (accelerometer, gyroscope, and compass) using Intel ISH (sensor hub).}
        % \item {[Zenbo]Android BSP development - porting capacitive touch sensor (GPIO, BIOS, Linux driver, Android HAL/Framework).}
        % \item {Android App unit test tool for sensor testing/debugging.}
        \item {Developed PID line-following and autonomous MCU-integrated docking algorithms for Zenbo/Zenbo Junior.}
        \item {Designed and deployed RobotAPI/SDK based on Android system for developer to access proprietary hardware features.}
        \item {Integrated battery, facial animation, and motor motion features into RobotFramework via Android System Services.}
        \item {Ported capacitive touch Linux drivers and configured GPIO/BIOS across HAL/Framework layers.}
        \item {Embedded motion sensors (accelerometer, gyroscope, and compass) via Intel ISH (Sensor Hub).}
      \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
